Zaca Fire Type Conversion

### 2020-10-08 Model Data Sheets and Code/Manuscript_Code.Rmd
minor change. tried running vsurf for pico data and got an error

@@

# select variables to be used in the model
pico_model2 <- pico %>% dplyr::select(rdnbr_tc, tmax, vpd_aug, cwd, rain, insolation, slope, aspect_transformed, TWI, ndmi_2006, evi_2006, years_since_burn, tmin_jan2007, ndmi_2006)

>>>>

#Extract prediction and response variables
pico.predictors <- pico_model[,2:ncol(pico_model)]
pico.response <- pico_model[,1]

#Run stepwise variable selection algorithm
pico.vsurf <- VSURF(x = pico.predictors, y = pico.response)

#Get names of selected variables
names(pico.predictors[pico.vsurf$varselect.thres])
names(pico.predictors[pico.vsurf$varselect.interp])
names(pico.predictors[pico$varselect.pred])

```
get error for some reason, but not with the MCF df :(

@@

# select variables to be used in the model
pico_model <- pico %>% dplyr::select(rdnbr_qualitative, tmax, vpd_aug, cwd, rain, insolation, slope, aspect_transformed, TWI, ndmi_2006, evi_2006, years_since_burn, tmin_jan2007, ndmi_2006)
